{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Draft was spell-checked.

\item \textbf{Slight Modification of the proposed {\it E}nKCF for
  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
  the flexibility of the ensemble of KCFs approach we propose. The
  original {\it E}nKCF is slighlty modified to track in low frame rate
  videos ($10$fps) dominated by large ego-motion. We do not integrate
  the particle filter in {\it E}nKCF2 as we test it on a temporally
  downsampled UAV123 dataset (UAV123$\_$10fps) including sequences
  with large ego-motion on a UAV platform. Particle Filter can be
  deployed in case the camera motion is known. The run-time
  performance decreases to $150$ fps, however, ratio of the video
  frame rate and run-time performance is similar to {\it E}nKCF. The
  proposed framework can be seen in fig.~\ref{Workflows}.
%\begin{figure*}[!t]
%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
%\label{Workflow_figure_EnKCF}
%\end{figure*}
%\begin{figure*}[!h]
%\centering
%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
%\label{Workflow_figure_EnKCF2}
%\end{figure*}

@@

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Fig.~\ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.
\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

@@

The order of running these three KCFs is important as each of these
filters aims at addressing different chanllenges while perserving
run-time performance as fast as possible. The \textit{target+large
  background} translation filter, $R_{t}^{L}$, is intended to run
right after the scale filter, $R_s$, runs which is applied at every
$k=5$ frames. We run these two filters this way because we want to
minimize any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other frames
before $R_{S}$ and right after two consecutive frames running
$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$, uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the workflow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. We do not have a seperate pseudeo-code for {\it E}nKCF2 as there are only two differences between 
  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
tracker due to large ego-motion. In the following section, we will briefly mention the theory
behind the KCF.
\begin{algorithm}[h]
\small
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{s}$ (Condition 1);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}
\begin{comment}
{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases \cite{henriques2012exploiting,henriques2015high}. Its computational efficiency arises from its use of the
discrete fourier transform of the circulant matrix and frequency
domain. The KCF tracker minimizes the regularized ridge regression function shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. 
\begin{comment}The primal solution in the
frequency domain is formulated as
%\begin{equation}
%w = (X^{T}X+\lambda)^{-1}y
%\label{eq:SpatialSolution}
%\end{equation}
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
where $X^{H}$ and $\lambda$represent the complex-conjugate of training
samples and regularization term. More documentation on the spatial and
fourier domain solutions can be found in \cite{henriques2015high}. The
MOSSE tracker uses one training sample centred at estimated position
of the target. This framework does not include enough background
information into the learned model,$w$. The application of the
circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg}
makes it possible to include many background patches at a similar
computational complexity. A circulant matrix includes the circularly
shifted patches of the positive training sample $x$ by a cylic shift
operator.

@@

Training shown in eq.~\ref{eq:FourierDualDomainSolution}
gives us $\hat{a}$ learned in time step $t$. We can accumulate
$\hat{a}$ over time to integrate more temporal information. This can
be expressed as
\begin{equation}
\hat{a}_{t} = (1-\beta)\hat{a}_{t-1} + \beta\hat{a}_{t}. 
\end{equation}
\end{comment}
Finally, detection step in multi-channel KCF framework is performed as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cylic shifts of the
first row of the kernel matrix.

\subsection{Particle Filter for Smoothing Transition of KCFs} \label{sc:PF}
As explained earlier, the {\it E}nKCF upates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential mishaps from
happening, we developed a Bayes filter that incorporates a target's
motion to smooth any outputs from the {\it E}nKCF. In particular, we
use a particle filter to estimate the target's image coordinate based
on the {\it E}nKCF's outputs. A particle filter is a sequential Monte
Carlo method that uses a finite number of particles or samples to
estimate the posterior probability density of a state of the system
\cite{thrun2005probabilistic}. In this study, the state represents a
target's pixel coordinates and its motion. In particular, the state of
the particle filter, $X_t$, is represented by $\lbrace x, y, v_{x},
v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates of the
target's centroid, $v_x$ and $v_y$ are the estimated velocity along
the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as:
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window as that of a confidence
map. Alternatively one can also use the euclidean distance of
particles to the location of maximum response of the confidence
map. This alternative, however, would result in drifts.

@@

\textbf{Performance on UAV123$\_$10fps Dataset.} We test our
slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps
version of the UAV123 dataset. The original dataset is already
dominated by fast object motion and large ego-motion. With
downsampling, it becomes very challenging with object and ego-motion
getting drastically larger. The performance of the proposed {\it
  E}nKCF2 tracker and other already mentioned trackers can be seen in
fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other
high-speed correlation filter based trackers including KCF, DSST by
about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than the MUSTER tracker.
\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123_10fps.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates. This dataset consists of temporally downsampled $123$ video sequences captured from a micro UAV.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

%\begin{figure}[!h]
%\centering
%\begin{tabular}{cc}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
%\end{tabular}
%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
%\label{fig:OTB100_DATASET}
%\end{figure}
%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm would be very attractive for any
mobile, unmanned robotic solutions on real-world applications. To make
such applications practical, those algorithms should run faster with
small footprint of computation resouce consumption. To this end, we
proposed an extension of KCF that deploys three KCFs in turn to
address the scale change and dynamic maneuvers of a target. The way we
ran three KCFs in a harmonious way optimal in a sense that efficiently
handled the scale change and effectively learned the translation of
the target. However, by doing so, our algorithm may introduce any
potential drifts. To prevent this from happening, we developed a Bayes
filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. Experimental results showed that the performance of ours are
70.10\% for precision on 20 pixels and 53.00\% for success rate for
OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123.

%--------------
%\section*{Acknowledgements}
%put stuff here for the accepted , but not the ICCV version

>>>>

\item \textbf{Slight Modification of the proposed {\it E}nKCF for
  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
  the flexibility of the ensemble of KCFs approach we propose. The
  original {\it E}nKCF is slightly modified to track in low frame rate
  videos ($10$fps) dominated by large ego-motion. We do not integrate
  the particle filter in {\it E}nKCF2 as we test it on a temporally
  down-sampled UAV123 dataset (UAV123$\_$10fps) including sequences
  with large ego-motion on a UAV platform. Particle Filter can be
  deployed in case the camera motion is known. The run-time
  performance decreases to $150$ fps, however, ratio of the video
  frame rate and run-time performance is similar to {\it E}nKCF. The
  proposed framework can be seen in fig.~\ref{Workflows}.
%\begin{figure*}[!t]
%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
%\label{Workflow_figure_EnKCF}
%\end{figure*}
%\begin{figure*}[!h]
%\centering
%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
%\label{Workflow_figure_EnKCF2}
%\end{figure*}

@@

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Fig.~\ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
element-wise multiplication, resulting in a scale estimation in a
higher speed.
\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

@@

The order of running these three KCFs is important as each of these
filters aims at addressing different challenges while preserving
run-time performance as fast as possible. The \textit{target+large
  background} translation filter, $R_{t}^{L}$, is intended to run
right after the scale filter, $R_s$, runs which is applied at every
$k=5$ frames. We run these two filters this way because we want to
minimize any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other frames
before $R_{S}$ and right after two consecutive frames running
$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$, uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the work-flow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. We do not have a separate pseudo-code for {\it E}nKCF2 as there are only two differences between 
  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
tracker due to large ego-motion. In the following section, we will briefly mention the theory
behind the KCF.
\begin{algorithm}[h]
\small
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{s}$ (Condition 1);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}
\begin{comment}
{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases \cite{henriques2012exploiting,henriques2015high}. Its computational efficiency arises from its use of the
discrete Fourier transform of the circulant matrix and frequency
domain. The KCF tracker minimizes the regularized ridge regression function shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and color into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. 
\begin{comment}The primal solution in the
frequency domain is formulated as
%\begin{equation}
%w = (X^{T}X+\lambda)^{-1}y
%\label{eq:SpatialSolution}
%\end{equation}
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
where $X^{H}$ and $\lambda$represent the complex-conjugate of training
samples and regularization term. More documentation on the spatial and
Fourier domain solutions can be found in \cite{henriques2015high}. The
MOSSE tracker uses one training sample centered at estimated position
of the target. This framework does not include enough background
information into the learned model,$w$. The application of the
circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg}
makes it possible to include many background patches at a similar
computational complexity. A circulant matrix includes the circularly
shifted patches of the positive training sample $x$ by a cyclic shift
operator.

@@

Training shown in eq.~\ref{eq:FourierDualDomainSolution}
gives us $\hat{a}$ learned in time step $t$. We can accumulate
$\hat{a}$ over time to integrate more temporal information. This can
be expressed as
\begin{equation}
\hat{a}_{t} = (1-\beta)\hat{a}_{t-1} + \beta\hat{a}_{t}. 
\end{equation}
\end{comment}
Finally, detection step in multi-channel KCF framework is performed as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

\subsection{Particle Filter for Smoothing Transition of KCFs} \label{sc:PF}
As explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential mishaps from
happening, we developed a Bayes filter that incorporates a target's
motion to smooth any outputs from the {\it E}nKCF. In particular, we
use a particle filter to estimate the target's image coordinate based
on the {\it E}nKCF's outputs. A particle filter is a sequential Monte
Carlo method that uses a finite number of particles or samples to
estimate the posterior probability density of a state of the system
\cite{thrun2005probabilistic}. In this study, the state represents a
target's pixel coordinates and its motion. In particular, the state of
the particle filter, $X_t$, is represented by $\lbrace x, y, v_{x},
v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates of the
target's centroid, $v_x$ and $v_y$ are the estimated velocity along
the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as:
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window as that of a confidence
map. Alternatively one can also use the Euclidean distance of
particles to the location of maximum response of the confidence
map. This alternative, however, would result in drifts.

@@

\textbf{Performance on UAV123$\_$10fps Dataset.} We test our
slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
UAV123$\_$10fps dataset. This dataset is down-sampled at $10$ fps
version of the UAV123 dataset. The original dataset is already
dominated by fast object motion and large ego-motion. With
down-sampling, it becomes very challenging with object and ego-motion
getting drastically larger. The performance of the proposed {\it
  E}nKCF2 tracker and other already mentioned trackers can be seen in
fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other
high-speed correlation filter based trackers including KCF, DSST by
about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than the MUSTER tracker.
\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123_10fps.pdf}}
\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates. This dataset consists of temporally downsampled $123$ video sequences captured from a micro UAV.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

%\begin{figure}[!h]
%\centering
%\begin{tabular}{cc}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
%\end{tabular}
%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
%\label{fig:OTB100_DATASET}
%\end{figure}
%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm would be economically and
practically, very attractive for any mobile, unmanned robotic
solutions on real-world applications. To make such pipelines more
realistic, however, those algorithms should run faster with small
footprint of computation resource consumption. To make an object
tracking algorithm with these practical requirements available, we
proposed an extension of KCF that essentially deploys three KCFs, in
turn, to address the scale change and dynamic maneuvers of a
target. The way we ran three KCFs in a harmonious way optimal in a
sense that efficiently handled the scale change and effectively
learned the translation of the target. However, by doing so, our
algorithm may introduce any potential drifts. To prevent this from
happening, we developed a Bayes filter, particle filter, to smooth the
transition between three KCFs. In particular, the particle filter
estimated the target's pixel coordinates using information about the
target's motion observed over frames. We used two publicly available
dataset to evaluate the performance of the proposed algorithm and
found that the performance of ours are 70.10\% for precision on 20
pixels and 53.00\% for success rate for OTB100 data, and 54.50\% and
40.2\% for UAV123 data. On average our method outperformed the
existing ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. 
%--------------
%\section*{Acknowledgements}
%put stuff here for the accepted , but not the ICCV version
